### 2024-11-10 paper_text.tex
fix long equation
fix ref to KD16
add two refs for mixtures

	\kappa_T^* & = & \frac{\epsilon}{\rho^{*2} W(0)} \left\{   \frac{Q_t^{-1/2}}{\beta W(0) g_4} \left[ \bar \rho_0 - 2 \left( - \frac{3M}{g_4} + \sqrt{Q_t} \right)^{\frac{1}{3}} \right] -1 \right\}.

@@

The third choice for the boundary between liquid-like and gas-like regions beyond CP is based on the condition $M=0$. Within the present approach, the condition $M=0$ holds along phase coexistence up to the critical point. Thus, the implementation of the condition $M=0$ above CP seems to be a natural continuation of the coexistence line into the supercritical region. On the other hand, taking into account the functional form of the grand partition function~\cite{KD16,KR09}, the condition of $M=0$ is equivalent to the absence of an external field in the Ising model. This analogy is interesting from the perspective of direct mapping between the Ising model and fluids~\cite{Kulinskii10jcp,BK11}. In Fig.~\ref{fig4} the separation line based on this condition $M=0$ is given by the dotted curve. In the critical region ($\tau<0.02$), beyond CP, the maxima locus of the response functions and the $M=0$ based line visually merge into a single line.

@@

	\bibitem{KozlovskiiDobush2016} M.~Kozlovskii, O.~Dobush.

@@

	\href{https://doi.org/10.1021/jp201872f}{Unified Picture for the Classical Laws of {B}atschinski and the Rectilinear Diameter for Molecular Fluids}. \textit{J. Phys. Chem. B} \textbf{115} 6061 (2011) [doi: 10.1021/jp201872f]

>>>>

	\kappa_T^* & = & \frac{\epsilon}{\rho^{*2} W(0)}
	\left\{   \frac{Q_t^{-1/2}}{\beta W(0) g_4} \right. \times
	&&\left. \times \left[ \bar \rho_0 - 2 \left( - \frac{3M}{g_4} + \sqrt{Q_t} \right)^{\frac{1}{3}} \right] -1 \right\}.
	\nonumber

@@

The third choice for the boundary between liquid-like and gas-like regions beyond CP is based on the condition $M=0$. Within the present approach, the condition $M=0$ holds along phase coexistence up to the critical point. Thus, the implementation of the condition $M=0$ above CP seems to be a natural continuation of the coexistence line into the supercritical region. On the other hand, taking into account the functional form of the grand partition function~\cite{KD16,KR09}, the condition of $M=0$ is equivalent to the absence of an external field in the Ising model. This analogy is interesting from the perspective of direct mapping between the Ising model and fluids~\cite{Kulinskii10jcp,BK11}, as well as from the consideration of other systems belonging to the Ising model class of universality, for example mixtures in criticality~\cite{OBP97,KD20b}. In Fig.~\ref{fig4} the separation line based on this condition $M=0$ is given by the dotted curve. In the critical region ($\tau<0.02$), beyond CP, the maxima locus of the response functions and the $M=0$ based line visually merge into a single line.

@@

	\bibitem{KD16} M.~Kozlovskii, O.~Dobush.

@@

	\href{https://doi.org/10.1021/jp201872f}{Unified picture for the classical laws of {B}atschinski and the rectilinear diameter for molecular fluids}. \textit{J. Phys. Chem. B} \textbf{115} 6061 (2011) [doi: 10.1021/jp201872f]
	\bibitem{OBP97} A.~Oleinikova, L.~Bulavin, V.~Pipich.
	\href{https://doi.org/10.1016/S0009-2614(97)00945-7}{Critical anomaly of shear viscosity in a mixture with an ionic impurity}. \textit{Chem. Phys. Lett.} \textbf{278} 121 (1997) [doi: 10.1016/S0009-2614(97)00945-7]
	\bibitem{KD20b} M.P.~Kozlovskii, O.A.~Dobush.
	\href{https://doi.org/10.15407/ujpe65.9.768}{Behavior of a binary asymmetric mixture of interacting particles in the supercritical region}. \textit{Ukr. J. Phys.} \textbf{65} 768 (2020) [doi: 10.15407/ujpe65.9.768]
